\sysfull

### 2017-08-11 paper/evaluation.tex
evaluation updated (fig 10 into table)

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/averageVirtualTaskSize}
	\caption{Average \sys virtual task size at fixed power per application. Top (green): number of coalesced tasks; bottom (red): average size of real task.}
	\label{fig:aveVirtuTaskSize}
\end{figure}

Then, we need to know how many tasks \sys can coalesce within a given execution scenario. We ran a subset of applications (split by tasks manually) with continuous power supply and measured the size of tasks for each application and the amount of tasks coalesced. Result is given in Figure~\ref{fig:aveVirtuTaskSize}. We see clearly that \sys manages to coalesce more tasks as individual tasks are small. As the size of individual task increases, e.g., as in the case of dft application, the number of coalesced tasks is also small. This result clearly shows that for the benefit of coalescing and for code portability, initial code should be split by \emph{as small tasks as possible}. This will help \sys to find the best possible virtual task size to minimise its runtime.

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|r|c|c|c|}
		\hline
		{} & bc & dft & cem \\
		\hline\hline
		Avg. no. coalesced tasks & 56 & 3 & 26 \\
		Avg. task size (MCU cycles) & 657 & 9680 & 722 \\
		\hline
	\end{tabular}
\caption{Average \sys virtual task size (at fixed power) per manually task split application.}
\label{tab:aveVirtuTaskSize}
\end{table}

%\begin{figure}
%	\centering
%	\includegraphics[width=\columnwidth]{figures/averageVirtualTaskSize}
%	\caption{Average \sys virtual task size at fixed power per application. Top (green): number of coalesced tasks; bottom (red): average size of real task.}
%	\label{fig:aveVirtuTaskSize}
%\end{figure}

Then, we need to know how many tasks \sys can coalesce within a given execution scenario. We ran a subset of applications (split by tasks manually) with continuous power supply and measured the size of tasks for each application and the amount of tasks coalesced. Result is given in Table~\ref{tab:aveVirtuTaskSize}. We see clearly that \sys manages to coalesce more tasks as individual tasks are small. As the size of individual task increases, e.g., as in the case of dft application, the number of coalesced tasks is also small. This result clearly shows that for the benefit of coalescing and for code portability, initial code should be split by \emph{as small tasks as possible}. This will help \sys to find the best possible virtual task size to minimise its runtime.
